Testing the simultaneous CI functions

### 2021-12-27 Code and miscellaneous/Interval_comparisons.Rmd
Checking code as there is something going on with the CI computation

#plot the simultaneous and pointwise intervals
a<-ggplot(pred, aes(x =Day,group=Group,color=Group,fill=Group)) +
    geom_path(aes(y=fit),lwd=2,show.legend = FALSE)+
    geom_ribbon(aes(ymin = lwrS, ymax = uprS), alpha = 0.2,show.legend = FALSE) +
    geom_ribbon(aes(ymin = lwrP, ymax = uprP), alpha = 0.2,show.legend = FALSE) +
    labs(y = "G. Simpson's code")+
   geom_hline(yintercept = 60,color="red")+
    geom_hline(yintercept = 20,color="red")+
    geom_hline(yintercept = 0,color="red")+
    theme_classic()+
    thm1

@@

ci <- confint(gam_02, parm = "s(Day)", partial_match = TRUE, type = "confidence")
## simultaneous interval
si <- confint(gam_02, parm = "s(Day)", type = "simultaneous", partial_match = TRUE)

@@

b<-ggplot(ci, aes(x = Day, y = est, group = smooth)) +
geom_line(lwd = 1,show.legend = FALSE) +
geom_ribbon(data = ci, mapping = aes(ymin = lower, ymax = upper, x = Day, group = smooth,fill = Group),
inherit.aes = FALSE, alpha = 0.7,
show.legend=FALSE) +
geom_ribbon(data = si,
mapping = aes(ymin = lower, ymax = upper, x = Day, group = smooth,fill =Group),
inherit.aes = FALSE, alpha = 0.4,
show.legend=FALSE)+
    geom_line(data=si,aes(Day,upper,color=Group),show.legend = FALSE)+
    geom_line(data=si,aes(Day,lower,color=Group),show.legend = FALSE)+
    geom_hline(yintercept = 60,color="red")+
    geom_hline(yintercept = 20,color="red")+
    geom_hline(yintercept = 0,color="red")+
    scale_x_continuous(breaks=c(0,2,5,7,10))+
     labs(y = "Our code")+
      theme_classic()+
        thm1

@@

```{r,plotting-data-and-intervals}
#plot both
c+a+b+scale_y_continuous(breaks=c(-20,0,20,40,60))

@@

>>>>

#plot the simultaneous and pointwise intervals
a<-ggplot(pred, aes(x =Day,group=Group,color=Group,fill=Group)) +
    geom_path(aes(y=fit),lwd=2,show.legend = FALSE)+
    geom_ribbon(aes(ymin = lwrS, ymax = uprS), alpha = 0.4,show.legend = FALSE) +
    geom_ribbon(aes(ymin = lwrP, ymax = uprP), alpha = 0.7,show.legend = FALSE) +
    labs(y = "G. Simpson's code")+
   geom_hline(yintercept = 60,color="red")+
    geom_hline(yintercept = 35.77,color="red")+
    geom_hline(yintercept = 20,color="red")+
    geom_hline(yintercept = 0,color="red")+
    scale_x_continuous(breaks=seq(1,10,1))+
    theme_classic()+
    thm1

@@

ci <- confint(gam_02, parm = "s(Day)", partial_match = TRUE, type ="confidence")
## simultaneous interval
si <- confint(gam_02, parm = "s(Day)", type = "simultaneous", partial_match = TRUE,nsim=10000)

@@

b<-ggplot(ci, aes(x = Day, y = est, group = smooth)) +
geom_line(lwd = 1,show.legend = FALSE) +
geom_ribbon(data = ci, mapping = aes(ymin = lower, ymax = upper, x = Day, group = smooth,fill = Group),
inherit.aes = FALSE, alpha = 0.7,
show.legend=FALSE) +
geom_ribbon(data = si,
mapping = aes(ymin = lower, ymax = upper, x = Day, group = smooth,fill =Group),
inherit.aes = FALSE, alpha = 0.4,
show.legend=FALSE)+
    geom_line(data=si,aes(Day,upper,color=Group),show.legend = FALSE)+
    geom_line(data=si,aes(Day,lower,color=Group),show.legend = FALSE)+
    geom_hline(yintercept = 60,color="red")+
    geom_hline(yintercept = 20,color="red")+
    geom_hline(yintercept = 0,color="red")+
    geom_hline(yintercept = 35.77,color="red")+
    scale_x_continuous(breaks=seq(1,10,1))+
     labs(y = "Our code")+
      theme_classic()+
        thm1

Additional test: use the approach we used initially to draw the confidence intervals, see if there's a difference:

```{r}

#creates a dataframe using the length of the covariates for the GAM
gam_predict <- expand_grid(Group = factor(c("Control", "Treatment")),
                         Day = seq(0, 10, by = 0.1),
                         subject=factor(rep(1:10)))

#adds the predictions to the grid and creates a confidence interval for GAM
gam_predict<-gam_predict%>%
    mutate(fit = predict(gam_02,gam_predict,se.fit = TRUE,type='response')$fit,
           se.fit = predict(gam_02, gam_predict,se.fit = TRUE,type='response')$se.fit)

#plot smooths and confidence interval for GAM
f3<-ggplot(data=dat_sim, aes(x=Day, y=StO2_sim, group=Group)) +
  geom_ribbon(aes( x=Day,ymin=(fit - 2*se.fit), 
                   ymax=(fit + 2*se.fit),
                   fill=Group
                   ),
              alpha=0.3,
              data=gam_predict,
            show.legend=FALSE,
                inherit.aes=FALSE) +
  geom_line(aes(y=fit,
                color=Group),
              size=1,data=gam_predict,
              show.legend = FALSE)+
    geom_hline(yintercept = 60,color="red")+
    geom_hline(yintercept = 20,color="red")+
    geom_hline(yintercept = 0,color="red")+
    geom_hline(yintercept = 35.77,color="red")+
  labs(y='previous method')+
    scale_x_continuous(breaks=seq(1,10,1))+
      theme_classic()+
    thm1

@@

```{r,plotting-data-and-intervals}
#plot both
c+a+b+f3+scale_y_continuous(breaks=c(-20,0,20,40,60))&theme_bw()

#plot the pointiwse intervals only

ggplot()+
geom_ribbon(aes(ymin = lwrP, ymax = uprP,x=Day,group=Group,fill='red'),
            alpha = 0.1,
            show.legend = FALSE,
            data=pred) +
    geom_ribbon(aes( x=Day,ymin=(fit - 2*se.fit), 
                   ymax=(fit + 2*se.fit),
                   group=Group
                   ),
              alpha=0.1,
              fill='green',
              data=gam_predict,
            show.legend=FALSE,
            inherit.aes = FALSE)+
    geom_ribbon(data = ci, mapping = aes(ymin = lower, ymax = upper, x = Day, group = smooth,fill = 'yellow'),
inherit.aes = FALSE, alpha = 0.8,
show.legend=FALSE)

ggplot()+
    geom_ribbon(aes(ymin = lwrS, ymax = uprS,x=Day,group=Group),
                fill='yellow',
                alpha = 0.4,
                show.legend = FALSE,data=pred) +
geom_ribbon(data = si,
mapping = aes(ymin = lower, ymax = upper, x = Day, group = smooth),
fill ='red',
inherit.aes = FALSE, alpha = 0.4,
show.legend=FALSE)

@@

From the plots, this is apparent:

The limits of the CI interval are the same in G.Simpson's code and in our original approach to the matter, they overlap perfectly. From our code however, the pointwise CI is slightly wider.

For the simultaneous CIs, the CI computed by G. Simpson's code is wider than the one we obtain using the `confint` function. Why is this?
